The landscape of chloroplast genome assembly tools

### 2020-05-19 manuscript/supplement.tex
Update to latest manuscript version

@@

\begin{landscape}
\setlength{\LTcapwidth}{1.5\textwidth}
\begin{longtable}{cccrrcc}
\caption[Summary real data set]{\textbf{Summary real data set.} List of real data sets used during our benchmark study. The tables was sorted by species name. Additionally, the table contains the accession for the Sequencing Read Archive (SRA Acc) and the accession of the used reference (Ref Acc). Moreover, the original number of read pairs (read pairs), the overall number of sequenced nucleotides (base pairs), and the mean read length (read len.) is given. Finally, the last column contains the information, if that data set was used for the check of the consistency.}\label{tab:real_dataset_details} \\
\hline
Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\
\hline
\endfirsthead
\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\ \hline
\endhead
\hline
\multicolumn{7}{r}{Continued on next page}\\
\endfoot
\endlastfoot
\input{sra_ref.tex}
\end{longtable}

\newpage
{\tiny
\captionof{table}{Docker images used in our benchmark setup.}
\label{tab:dockerimages_suppl}
\centering
\begin{tabular}{ccc}
        \hline
          Tool & Image name and tag & SHA256 Checksum   \\ \hline
          \ce & \dockerce & \dockercesha \\
          \cassp & \dockercassp & \dockercasspsha \\
          \fp & \dockerfp & \dockerfpsha \\
          \go & \dockergo & \dockergosha \\
          \ioga & \dockerioga & \dockeriogasha \\
          \np & \dockernp & \dockernpsha \\
          \oa & \dockeroa & \dockeroasha \\ \hline
      \end{tabular}
}
\end{landscape}

\begin{table}[ht]
\caption{Performance metrics input size 25K}
\label{tab:perform25K_suppl}
\centering
\begin{tabular}{rlrrrr}
  \hline
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
  \hline
1 & CAP &   1 & 113.32 & 0.31 & 0.06 \\ 
  2 & CAP &   2 & 166.60 & 0.26 & 0.05 \\ 
  3 & CAP &   4 & 305.99 & 0.26 & 0.05 \\ 
  4 & CAP &   8 & 569.12 & 0.37 & 0.06 \\ 
  5 & CE &   1 & 111.49 & 3.41 & 0.07 \\ 
  6 & CE &   2 & 199.12 & 3.41 & 0.07 \\ 
  7 & CE &   4 & 343.22 & 3.41 & 0.07 \\ 
  8 & CE &   8 & 509.51 & 3.41 & 0.07 \\ 
  9 & Fast-Plast &   1 & 118.31 & 0.77 & 0.30 \\ 
  10 & Fast-Plast &   2 & 213.57 & 0.77 & 0.31 \\ 
  11 & Fast-Plast &   4 & 379.27 & 0.77 & 0.32 \\ 
  12 & Fast-Plast &   8 & 657.20 & 0.77 & 0.35 \\ 
  13 & GetOrganelle &   1 & 111.39 & 0.38 & 0.05 \\ 
  14 & GetOrganelle &   2 & 170.30 & 0.32 & 0.05 \\ 
  15 & GetOrganelle &   4 & 242.27 & 0.31 & 0.06 \\ 
  16 & GetOrganelle &   8 & 346.98 & 0.31 & 0.07 \\ 
  17 & IOGA &   1 & 118.12 & 18.61 & 6.25 \\ 
  18 & IOGA &   2 & 224.74 & 17.88 & 6.26 \\ 
  19 & IOGA &   4 & 394.98 & 16.62 & 5.60 \\ 
  20 & IOGA &   8 & 733.11 & 21.76 & 11.13 \\ 
  21 & NOVOPlasty &   1 & 78.38 & 0.04 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 86.64 & 0.04 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 86.50 & 0.04 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 87.32 & 0.04 & 0.00 \\ 
  25 & org.ASM &   1 & 112.08 & 0.79 & 0.03 \\ 
  26 & org.ASM &   2 & 115.44 & 0.79 & 0.03 \\ 
  27 & org.ASM &   4 & 105.09 & 0.79 & 0.03 \\ 
  28 & org.ASM &   8 & 105.78 & 0.79 & 0.03 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Performance metrics input size 250K}
\label{tab:perform250K_suppl}
\centering
\begin{tabular}{rlrrrr}
  \hline
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
  \hline
1 & CAP &   1 & 114.38 & 0.90 & 0.65 \\ 
  2 & CAP &   2 & 204.39 & 0.93 & 0.65 \\ 
  3 & CAP &   4 & 337.09 & 0.97 & 0.65 \\ 
  4 & CAP &   8 & 652.75 & 1.08 & 0.65 \\ 
  5 & CE &   1 & 117.57 & 3.96 & 0.63 \\ 
  6 & CE &   2 & 230.35 & 3.96 & 0.63 \\ 
  7 & CE &   4 & 414.25 & 3.96 & 0.63 \\ 
  8 & CE &   8 & 755.76 & 3.97 & 0.63 \\ 
  9 & Fast-Plast &   1 & 118.81 & 1.40 & 0.78 \\ 
  10 & Fast-Plast &   2 & 234.12 & 2.25 & 0.78 \\ 
  11 & Fast-Plast &   4 & 425.89 & 2.32 & 0.79 \\ 
  12 & Fast-Plast &   8 & 845.94 & 2.52 & 0.79 \\ 
  13 & GetOrganelle &   1 & 117.94 & 1.07 & 0.40 \\ 
  14 & GetOrganelle &   2 & 227.05 & 1.13 & 0.40 \\ 
  15 & GetOrganelle &   4 & 403.35 & 1.08 & 0.40 \\ 
  16 & GetOrganelle &   8 & 747.20 & 1.03 & 0.39 \\ 
  17 & IOGA &   1 & 118.62 & 12.03 & 4.01 \\ 
  18 & IOGA &   2 & 234.09 & 9.71 & 4.01 \\ 
  19 & IOGA &   4 & 420.77 & 10.09 & 3.48 \\ 
  20 & IOGA &   8 & 842.57 & 19.21 & 9.45 \\ 
  21 & NOVOPlasty &   1 & 111.97 & 0.32 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 115.07 & 0.32 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 116.42 & 0.31 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 115.86 & 0.31 & 0.00 \\ 
  25 & org.ASM &   1 & 118.10 & 0.93 & 0.06 \\ 
  26 & org.ASM &   2 & 161.76 & 0.93 & 0.06 \\ 
  27 & org.ASM &   4 & 163.01 & 0.93 & 0.06 \\ 
  28 & org.ASM &   8 & 160.74 & 0.93 & 0.06 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Performance metrics input size 2.5M}
\label{tab:perform2.5M_suppl}
\centering
\begin{tabular}{rlrrrr}
  \hline
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
 \hline
1 & CAP &   1 & 118.80 & 6.83 & 6.59 \\ 
  2 & CAP &   2 & 209.22 & 7.58 & 6.59 \\ 
  3 & CAP &   4 & 357.36 & 7.25 & 6.59 \\ 
  4 & CAP &   8 & 683.71 & 6.99 & 6.59 \\ 
  5 & CE &   1 & 118.78 & 5.34 & 2.01 \\ 
  6 & CE &   2 & 234.82 & 5.34 & 2.01 \\ 
  7 & CE &   4 & 415.74 & 5.28 & 2.09 \\ 
  8 & CE &   8 & 844.95 & 5.34 & 2.01 \\ 
  9 & Fast-Plast &   1 & 119.24 & 6.80 & 5.80 \\ 
  10 & Fast-Plast &   2 & 237.34 & 6.98 & 5.82 \\ 
  11 & Fast-Plast &   4 & 443.27 & 8.02 & 5.69 \\ 
  12 & Fast-Plast &   8 & 872.07 & 8.87 & 5.69 \\ 
  13 & GetOrganelle &   1 & 118.91 & 5.25 & 3.31 \\ 
  14 & GetOrganelle &   2 & 235.18 & 5.26 & 3.31 \\ 
  15 & GetOrganelle &   4 & 420.10 & 5.44 & 3.31 \\ 
  16 & GetOrganelle &   8 & 845.13 & 6.07 & 3.31 \\ 
  17 & IOGA &   1 & 119.46 & 18.64 & 8.83 \\ 
  18 & IOGA &   2 & 237.22 & 21.24 & 10.19 \\ 
  19 & IOGA &   4 & 425.50 & 18.71 & 10.56 \\ 
  20 & IOGA &   8 & 857.29 & 25.23 & 16.51 \\ 
  21 & NOVOPlasty &   1 & 112.67 & 2.69 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 117.77 & 2.58 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 117.40 & 2.74 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 117.28 & 2.74 & 0.00 \\ 
  25 & org.ASM &   1 & 118.73 & 2.63 & 0.37 \\ 
  26 & org.ASM &   2 & 184.53 & 2.63 & 0.37 \\ 
  27 & org.ASM &   4 & 177.03 & 2.63 & 0.37 \\ 
  28 & org.ASM &   8 & 176.25 & 2.63 & 0.37 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\usepackage{tabularx}
\usepackage{booktabs}

@@

\begin{table}[ht]
\caption{Sequencing Read Archive and Genbank accessions for novel chloroplast genomes}
\label{tab:accessions_suppl}
\centering
\begin{tabular}{cccc}\toprule
Species & SRA-Accession & Assembler & Genbank-Accession \\\midrule
\plant{At} & AAAA & AAA & AAAA \\\bottomrule
\end{tabular}
\end{table}

\begin{landscape}
\setlength{\LTcapwidth}{1.5\textwidth}
\begin{longtable}{cccrrcc}
\caption[Summary real data set]{\textbf{Summary real data set.} List of real data sets used during our benchmark study. The tables was sorted by species name. Additionally, the table contains the accession for the Sequencing Read Archive (SRA Acc) and the accession of the used reference (Ref Acc). Moreover, the original number of read pairs (read pairs), the overall number of sequenced nucleotides (base pairs), and the mean read length (read len.) is given. Finally, the last column contains the information, if that data set was used for the check of the consistency.}\label{tab:real_dataset_details} \\
\toprule
Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\\midrule
\endfirsthead
\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\ \midrule
\endhead
\bottomrule
\multicolumn{7}{r}{Continued on next page}\\
\endfoot
\endlastfoot
\input{sra_ref.tex}
\end{longtable}

\newpage
{\tiny
\captionof{table}{Docker images used in our benchmark setup.}
\label{tab:dockerimages_suppl}
\centering
\begin{tabular}{ccc}
        \toprule
          Tool & Image name and tag & SHA256 Checksum   \\ \midrule
          \ce & \dockerce & \dockercesha \\
          \cassp & \dockercassp & \dockercasspsha \\
          \fp & \dockerfp & \dockerfpsha \\
          \go & \dockergo & \dockergosha \\
          \ioga & \dockerioga & \dockeriogasha \\
          \np & \dockernp & \dockernpsha \\
          \oa & \dockeroa & \dockeroasha \\ \bottomrule
      \end{tabular}
}
\end{landscape}

\begin{table}[ht]
\caption{Performance metrics input size 25K}
\label{tab:perform25K_suppl}
\centering
\begin{tabular}{rlrrrr}
  \toprule
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
  \midrule
1 & CAP &   1 & 113.32 & 0.31 & 0.06 \\ 
  2 & CAP &   2 & 166.60 & 0.26 & 0.05 \\ 
  3 & CAP &   4 & 305.99 & 0.26 & 0.05 \\ 
  4 & CAP &   8 & 569.12 & 0.37 & 0.06 \\ 
  5 & CE &   1 & 111.49 & 3.41 & 0.07 \\ 
  6 & CE &   2 & 199.12 & 3.41 & 0.07 \\ 
  7 & CE &   4 & 343.22 & 3.41 & 0.07 \\ 
  8 & CE &   8 & 509.51 & 3.41 & 0.07 \\ 
  9 & Fast-Plast &   1 & 118.31 & 0.77 & 0.30 \\ 
  10 & Fast-Plast &   2 & 213.57 & 0.77 & 0.31 \\ 
  11 & Fast-Plast &   4 & 379.27 & 0.77 & 0.32 \\ 
  12 & Fast-Plast &   8 & 657.20 & 0.77 & 0.35 \\ 
  13 & GetOrganelle &   1 & 111.39 & 0.38 & 0.05 \\ 
  14 & GetOrganelle &   2 & 170.30 & 0.32 & 0.05 \\ 
  15 & GetOrganelle &   4 & 242.27 & 0.31 & 0.06 \\ 
  16 & GetOrganelle &   8 & 346.98 & 0.31 & 0.07 \\ 
  17 & IOGA &   1 & 118.12 & 18.61 & 6.25 \\ 
  18 & IOGA &   2 & 224.74 & 17.88 & 6.26 \\ 
  19 & IOGA &   4 & 394.98 & 16.62 & 5.60 \\ 
  20 & IOGA &   8 & 733.11 & 21.76 & 11.13 \\ 
  21 & NOVOPlasty &   1 & 78.38 & 0.04 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 86.64 & 0.04 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 86.50 & 0.04 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 87.32 & 0.04 & 0.00 \\ 
  25 & org.ASM &   1 & 112.08 & 0.79 & 0.03 \\ 
  26 & org.ASM &   2 & 115.44 & 0.79 & 0.03 \\ 
  27 & org.ASM &   4 & 105.09 & 0.79 & 0.03 \\ 
  28 & org.ASM &   8 & 105.78 & 0.79 & 0.03 \\ 
   \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Performance metrics input size 250K}
\label{tab:perform250K_suppl}
\centering
\begin{tabular}{rlrrrr}
  \toprule
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
  \midrule
1 & CAP &   1 & 114.38 & 0.90 & 0.65 \\ 
  2 & CAP &   2 & 204.39 & 0.93 & 0.65 \\ 
  3 & CAP &   4 & 337.09 & 0.97 & 0.65 \\ 
  4 & CAP &   8 & 652.75 & 1.08 & 0.65 \\ 
  5 & CE &   1 & 117.57 & 3.96 & 0.63 \\ 
  6 & CE &   2 & 230.35 & 3.96 & 0.63 \\ 
  7 & CE &   4 & 414.25 & 3.96 & 0.63 \\ 
  8 & CE &   8 & 755.76 & 3.97 & 0.63 \\ 
  9 & Fast-Plast &   1 & 118.81 & 1.40 & 0.78 \\ 
  10 & Fast-Plast &   2 & 234.12 & 2.25 & 0.78 \\ 
  11 & Fast-Plast &   4 & 425.89 & 2.32 & 0.79 \\ 
  12 & Fast-Plast &   8 & 845.94 & 2.52 & 0.79 \\ 
  13 & GetOrganelle &   1 & 117.94 & 1.07 & 0.40 \\ 
  14 & GetOrganelle &   2 & 227.05 & 1.13 & 0.40 \\ 
  15 & GetOrganelle &   4 & 403.35 & 1.08 & 0.40 \\ 
  16 & GetOrganelle &   8 & 747.20 & 1.03 & 0.39 \\ 
  17 & IOGA &   1 & 118.62 & 12.03 & 4.01 \\ 
  18 & IOGA &   2 & 234.09 & 9.71 & 4.01 \\ 
  19 & IOGA &   4 & 420.77 & 10.09 & 3.48 \\ 
  20 & IOGA &   8 & 842.57 & 19.21 & 9.45 \\ 
  21 & NOVOPlasty &   1 & 111.97 & 0.32 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 115.07 & 0.32 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 116.42 & 0.31 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 115.86 & 0.31 & 0.00 \\ 
  25 & org.ASM &   1 & 118.10 & 0.93 & 0.06 \\ 
  26 & org.ASM &   2 & 161.76 & 0.93 & 0.06 \\ 
  27 & org.ASM &   4 & 163.01 & 0.93 & 0.06 \\ 
  28 & org.ASM &   8 & 160.74 & 0.93 & 0.06 \\ 
   \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Performance metrics input size 2.5M}
\label{tab:perform2.5M_suppl}
\centering
\begin{tabular}{rlrrrr}
  \toprule
 & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
 \midrule
1 & CAP &   1 & 118.80 & 6.83 & 6.59 \\ 
  2 & CAP &   2 & 209.22 & 7.58 & 6.59 \\ 
  3 & CAP &   4 & 357.36 & 7.25 & 6.59 \\ 
  4 & CAP &   8 & 683.71 & 6.99 & 6.59 \\ 
  5 & CE &   1 & 118.78 & 5.34 & 2.01 \\ 
  6 & CE &   2 & 234.82 & 5.34 & 2.01 \\ 
  7 & CE &   4 & 415.74 & 5.28 & 2.09 \\ 
  8 & CE &   8 & 844.95 & 5.34 & 2.01 \\ 
  9 & Fast-Plast &   1 & 119.24 & 6.80 & 5.80 \\ 
  10 & Fast-Plast &   2 & 237.34 & 6.98 & 5.82 \\ 
  11 & Fast-Plast &   4 & 443.27 & 8.02 & 5.69 \\ 
  12 & Fast-Plast &   8 & 872.07 & 8.87 & 5.69 \\ 
  13 & GetOrganelle &   1 & 118.91 & 5.25 & 3.31 \\ 
  14 & GetOrganelle &   2 & 235.18 & 5.26 & 3.31 \\ 
  15 & GetOrganelle &   4 & 420.10 & 5.44 & 3.31 \\ 
  16 & GetOrganelle &   8 & 845.13 & 6.07 & 3.31 \\ 
  17 & IOGA &   1 & 119.46 & 18.64 & 8.83 \\ 
  18 & IOGA &   2 & 237.22 & 21.24 & 10.19 \\ 
  19 & IOGA &   4 & 425.50 & 18.71 & 10.56 \\ 
  20 & IOGA &   8 & 857.29 & 25.23 & 16.51 \\ 
  21 & NOVOPlasty &   1 & 112.67 & 2.69 & 0.00 \\ 
  22 & NOVOPlasty &   2 & 117.77 & 2.58 & 0.00 \\ 
  23 & NOVOPlasty &   4 & 117.40 & 2.74 & 0.00 \\ 
  24 & NOVOPlasty &   8 & 117.28 & 2.74 & 0.00 \\ 
  25 & org.ASM &   1 & 118.73 & 2.63 & 0.37 \\ 
  26 & org.ASM &   2 & 184.53 & 2.63 & 0.37 \\ 
  27 & org.ASM &   4 & 177.03 & 2.63 & 0.37 \\ 
  28 & org.ASM &   8 & 176.25 & 2.63 & 0.37 \\ 
   \bottomrule
\end{tabular}
\end{table}

\begin{landscape}
\begin{longtable}{lcccp{7cm}c}
\caption[Novel data set]{\textbf{Novel data set.}}\label{tab:novels_supp} \\
  \toprule
 SRA Accession & Depth & TaxID & Rank & Related References with Depth & Status \\
 \midrule
\endfirsthead
\multicolumn{6}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
 SRA Accession & Depth & TaxID & Rank & Related References with Depth & Status \\
 \midrule
\endhead
\bottomrule
\multicolumn{6}{r}{Continued on next page}\\
\endfoot
\endlastfoot
DRR053713 & 3 & 71243 & order & NC\_033350(3) & success \\
DRR057122 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
DRR106816 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
ERR1917165 & 5 & 4118 & family & NC\_009808(3) NC\_026703(3) NC\_031159(3) NC\_034670(3) & success \\
ERR2003066 & 3 & 721789 & tribe & NC\_018767(3) NC\_019601(3) NC\_019602(3) NC\_034347(3) NC\_015206(4) NC\_018766(4) & success \\
ERR2744401 & 5 & 156152 & family & NC\_028519(3) NC\_028520(3) NC\_031345(3) NC\_034688(3) NC\_031153(4) NC\_031344(4) & success \\
ERR2744402 & 4 & 156152 & family & NC\_028519(3) NC\_028520(3) NC\_031345(3) NC\_034688(3) NC\_031153(4) NC\_031344(4) & success \\
ERR3089127 & 4 & 102810 & tribe & NC\_020092(3) NC\_020320(3) NC\_020607(3) NC\_025910(3) NC\_030785(3) NC\_031399(3) NC\_031400(3) NC\_034683(3) NC\_034851(3) & success \\
SRR2154064 & 4 & 4210 & family & NC\_027835(4) NC\_034648(4) NC\_007578(5) NC\_007977(5) NC\_010601(5) NC\_013553(5) NC\_015543(5) NC\_015621(5) NC\_020092(5) NC\_020320(5) NC\_020607(5) NC\_023107(5) NC\_023108(5) NC\_023109(5) NC\_023110(5) NC\_023111(5) NC\_023112(5) NC\_023113(5) NC\_023114(5) NC\_023833(5) NC\_024286(5) NC\_025910(5) NC\_027113(5) NC\_027434(5) NC\_028005(5) NC\_028006(5) NC\_028027(5) NC\_029465(5) NC\_030173(5) NC\_030275(5) NC\_030772(5) NC\_030773(5) NC\_030783(5) NC\_030785(5) NC\_031395(5) NC\_031396(5) NC\_031399(5) NC\_031400(5) NC\_031815(5) NC\_031816(5) NC\_031833(5) NC\_031853(5) NC\_031898(5) NC\_032056(5) NC\_032057(5) NC\_034320(5) NC\_034321(5) NC\_034322(5) NC\_034323(5) NC\_034324(5) NC\_034325(5) NC\_034326(5) NC\_034327(5) NC\_034328(5) NC\_034683(5) NC\_034810(5) NC\_034811(5) NC\_034812(5) NC\_034813(5) NC\_034814(5) NC\_034815(5) NC\_034816(5) NC\_034817(5) NC\_034818(5) NC\_034819(5) NC\_034820(5) NC\_034821(5) NC\_034822(5) NC\_034823(5) NC\_034824(5) NC\_034825(5) NC\_034827(5) NC\_034828(5) NC\_034829(5) NC\_034830(5) NC\_034831(5) NC\_034832(5) NC\_034847(5) NC\_034848(5) NC\_034849(5) NC\_034850(5) NC\_034851(5) NC\_034852(5) NC\_034853(5) NC\_034854(5) NC\_034856(5) NC\_034857(5) NC\_034858(5) NC\_034859(5) NC\_034860(5) NC\_034861(5) NC\_034862(5) NC\_034864(5) NC\_034865(5) NC\_034866(5) NC\_034867(5) NC\_034868(5) NC\_034869(5) NC\_034870(5) NC\_034871(5) NC\_034872(5) NC\_034873(5) NC\_034874(5) NC\_034875(5) NC\_034876(5) NC\_034877(5) NC\_034878(5) NC\_034879(5) NC\_034880(5) NC\_034881(5) NC\_034882(5) NC\_034883(5) NC\_034884(5) NC\_034885(5) NC\_034886(5) NC\_034887(5) NC\_034888(5) NC\_034889(5) NC\_034891(5) NC\_034892(5) NC\_034893(5) NC\_034894(5) NC\_034895(5) NC\_034896(5) NC\_034897(5) NC\_034898(5) NC\_034899(5) NC\_034900(5) NC\_034901(5) NC\_034902(5) NC\_034903(5) NC\_034996(5) & success \\
SRR2176133 & 3 & 40550 & order & NC\_026786(3) NC\_027659(3) & success \\
SRR2401791 & 4 & 91888 & no rank & NC\_016433(4) NC\_021449(4) NC\_023463(4) NC\_025652(4) NC\_025653(4) NC\_029719(4) NC\_030212(4) NC\_031435(4) NC\_031436(4) NC\_008407(5) NC\_009808(5) NC\_013707(5) NC\_020098(5) NC\_021111(5) NC\_022859(5) NC\_023102(5) NC\_023115(5) NC\_023131(5) NC\_023132(5) NC\_023464(5) NC\_023465(5) NC\_024845(5) NC\_025641(5) NC\_025642(5) NC\_025651(5) NC\_025787(5) NC\_026202(5) NC\_026291(5) NC\_026703(5) NC\_027262(5) NC\_027838(5) NC\_027955(5) NC\_028519(5) NC\_028520(5) NC\_028533(5) NC\_029700(5) NC\_031159(5) NC\_031345(5) NC\_031437(5) NC\_031441(5) NC\_031442(5) NC\_031443(5) NC\_031444(5) NC\_031445(5) NC\_033534(5) NC\_034308(5) NC\_034309(5) NC\_034310(5) NC\_034311(5) NC\_034312(5) NC\_034670(5) NC\_034688(5) NC\_034691(5) NC\_034693(5) NC\_034694(5) NC\_034695(5) NC\_035000(5) NC\_001879(6) NC\_004561(6) NC\_007500(6) NC\_007602(6) NC\_007943(6) NC\_008096(6) NC\_015401(6) NC\_015604(6) NC\_015608(6) NC\_015623(6) NC\_016068(6) NC\_018117(6) NC\_018552(6) NC\_022451(6) NC\_024261(6) NC\_024292(6) NC\_025657(6) NC\_026551(6) NC\_026563(6) NC\_026567(6) NC\_026570(6) NC\_026574(6) NC\_026694(6) NC\_026726(6) NC\_026906(6) NC\_027099(6) NC\_027177(6) NC\_027441(6) NC\_027442(6) NC\_028007(6) NC\_028009(6) NC\_028069(6) NC\_028070(6) NC\_028614(6) NC\_029370(6) NC\_029746(6) NC\_029817(6) NC\_029818(6) NC\_029819(6) NC\_029820(6) NC\_029821(6) NC\_029822(6) NC\_029823(6) NC\_029824(6) NC\_029825(6) NC\_029833(6) NC\_030044(6) NC\_030056(6) NC\_030167(6) NC\_030168(6) NC\_030171(6) NC\_030177(6) NC\_030178(6) NC\_030185(6) NC\_030207(6) NC\_030282(6) NC\_030319(6) NC\_030543(6) NC\_030755(6) NC\_030756(6) NC\_030757(6) NC\_031153(6) NC\_031155(6) NC\_031344(6) NC\_031433(6) NC\_031434(6) NC\_031805(6) NC\_031874(6) NC\_032054(6) NC\_032724(6) NC\_033354(6) NC\_033524(6) NC\_033525(6) NC\_033526(6) NC\_033527(6) NC\_034698(6) NC\_034951(6) NC\_035143(6) AC\_000188(7) NC\_007898(7) NC\_016468(7) NC\_020431(7) NC\_021423(7) NC\_022431(7) NC\_022432(7) NC\_025655(7) NC\_025656(7) NC\_025658(7) NC\_026876(7) NC\_026877(7) NC\_026878(7) NC\_026879(7) NC\_026880(7) NC\_026881(7) NC\_026882(7) NC\_027259(7) NC\_029459(7) NC\_029460(7) NC\_031852(7) NC\_034660(7) NC\_035233(7) NC\_008535(8) NC\_030053(8) & success \\
SRR2531270 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR2531276 & 4 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR2531278 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR2531280 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR2531284 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR2531289 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
SRR4124062 & 7 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
SRR4124063 & 6 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
SRR4124078 & 6 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
